---
title: "Cecilia_AiB - picking teams"
author: "Cecilia Nok Sze Cheung"
date: "11 December 2016"
output: html_document
---

```{r knitr, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Steven's stuff


```{r setup, include=FALSE}
library(reshape2)
library(lsa)
library(ggplot2)
library(pander)
```

```{r echo=FALSE}
# load data
picks.data <- read.csv("peoplepickinganonymised.csv")
```

```{r echo=FALSE}
# a bit of exploratory analysis

sequence <- c(0,60,120,240)
count <- 0

for (i in 1:60) {
  count <- 1
  for (j in sequence) {
    assign(paste("candidate", i, count , sep=""), picks.data[, 3+i+j])
    count <- count + 1
  }
  
}

#paste("id",1,sep = '')

```

```{r echo=FALSE}
# cosine similarity

# first create an empty matrix that will be populated with the cosine similarity results
mat.cosine <- matrix(0, 60, 5)
mat.cosine2 <- matrix(0, 60, 5)

# subset data to only include the picks
sub.data <- picks.data[, 4:length(picks.data)]

diag(sub.data[ , 1:60]) <- 0
diag(sub.data[ , 61:120]) <- 0
diag(sub.data[ , 121:180]) <- 0
diag(sub.data[ , 181:240]) <- 0
diag(sub.data[ , 241:300]) <- 0

# calculate cosine similarity and populate matrix
for (id in 1:nrow(sub.data)) {
  
  # extract all the vectors needed to calculate the cosine similarities
  friend <- as.numeric(sub.data[id, 1:60])   # skip the influence picks
  creativity <- as.numeric(sub.data[id, 121:180])
  influence <- as.numeric(sub.data[id, 181:240])
  implementation <- as.numeric(sub.data[id, 241:300])
  
  # populate cosine matrix
  mat.cosine[id,2] <- cosine(friend, friend)
  mat.cosine[id,3] <- cosine(friend, creativity)
  mat.cosine[id,4] <- cosine(friend, influence)
  mat.cosine[id,5] <- cosine(friend, implementation)
}

# manual calculation for cosine similarity
cosine.sim <- function(x,y) {
  x %*% y / sqrt(x%*%x * y%*%y)
}

# check if results are the same using built function
for (id in 1:nrow(sub.data)) {
  
  # extract all the vectors needed to calculate the cosine similarities
  friend <- as.numeric(sub.data[id, 1:60])   # skip the influence picks
  creativity <- as.numeric(sub.data[id, 121:180])
  influence <- as.numeric(sub.data[id, 181:240])
  implementation <- as.numeric(sub.data[id, 241:300])
  
  # populate cosine matrix
  mat.cosine2[id,2] <- cosine.sim(friend, friend)
  mat.cosine2[id,3] <- cosine.sim(friend, creativity)
  mat.cosine2[id,4] <- cosine.sim(friend, influence)
  mat.cosine2[id,5] <- cosine.sim(friend, implementation)
}

# mat.cosine == mat.cosine2, returns TRUE

# calculate the mean cosine similarity for each ID, without Friend_Friend column
means <- rowMeans(mat.cosine[,3:5])

# combine means to cosine matrix
mat.cosineM <- cbind(mat.cosine, means)

# convert to dataframe, add column names, populate ID column
data.cosine <- data.frame(mat.cosineM)

names <- c("id", "Friend_Friend", "Friend_Creativity", "Friend_Influence", "Friend_Implementation", "Average")
colnames(data.cosine) <- names

data.cosine$id <- 1:60

# order "average" decreasing
cosine.order <- data.cosine[order(-data.cosine$Average),]

# z-score function
z.score <- function(x, mean, sd) {
  (x - mean) / sd
}

# mean of cosine scores
mean.cosine <- mean(cosine.order$Average, na.rm = TRUE)

# sd of cosine scores
sd.cosine <- sd(cosine.order$Average, na.rm = TRUE)

# apply z-score function to calculate z-score
cosine.order$Z.score <- sapply(cosine.order$Average, z.score, mean = mean.cosine,sd=sd.cosine)
```

```{r echo=FALSE, fig.width = 10, fig.align = "center"}
# create bins in cosine.order
cosine.order$bin <- cut(cosine.order$Average, breaks = 5, labels = c("(0,0.2]","(0.2,0.4]", "(0.4,0.6]","(0.6,0.8]","(0.8,1]"))

# plot histogram of average cosine similarities
ggplot(na.omit(cosine.order), aes(bin, fill = bin)) +
  geom_bar() +
  labs(x = "Cosine Similarity", y = "Count", title = "Average Cosine Similarity Frequency") +
  scale_fill_brewer(palette = "Blues",direction = -1, guide=FALSE)
```

The graph above shows the average cosine similarity for each ID. As can be seen, over 20 IDs display a high level of flexibility in picking teams for different tasks. The average cosine similarity was calculated using each IDs social picks as benchmark. These picks were then compared to each IDs picks for different tasks. Three IDs have an average cosine similarity of 1, indicating very low levels of flexibility. 

```{r echo=FALSE, fig.width = 10, fig.align = "center", fig.height=8}
# plot each IDs average cosine score
ggplot(na.omit(cosine.order), aes(x = reorder(factor(id), Average), y = Average, fill = Average)) +
  geom_bar(stat="identity") +
  coord_flip() +
  labs(x = "ID", y = "Average Cosine Similarity", title = "Average Cosine Similarity by ID") +
  scale_fill_distiller(palette = "Blues", guide=FALSE, direction = 1)
```

```{r echo=FALSE, fig.align="center"}
# subset cosine table to only include ID, average, z-score
cosine.table <- cosine.order[, c("id","Average","Z.score")]
panderOptions("digits", 3)
pander(cosine.table)

### write.csv(cosine.order, file = "cosine.csv")
```



## Analysis - picking leaders

```{r}
library(reshape2)
library(plyr)

```


```{r}
fulldata <- read.csv("peoplepickinganonymised.csv")
```


```{r}
#cleaning up and wrangling data

fulldata[, c(1:303)] <- sapply(fulldata[, c(1:303)], as.numeric)

#make seperate df for each component, set diagonal to 0 and sum up columns
friends <- fulldata[,4:63] 
friends[row(friends) == col(friends) ] <- 0
friends["Total",] <- colSums(friends)

advice <- fulldata[,64:123]
advice[row(advice) == col(advice) ] <- 0
advice["Total",] <- colSums(advice)


creativity <- fulldata[,124:183]
creativity[row(creativity) == col(creativity) ] <- 0
creativity["Total",] <- colSums(creativity)

implementation <- fulldata[,184:243]
implementation[row(implementation) == col(implementation) ] <- 0
implementation["Total",] <- colSums(implementation)


influence <- fulldata[,244:303]
influence[row(influence) == col(influence) ] <- 0
influence["Total",] <- colSums(influence)


#transform dataframes and turn back into df
friendstr <- as.data.frame(t(friends))
advicetr <- as.data.frame(t(advice))
creativitytr <- as.data.frame(t(creativity))
implementationtr <- as.data.frame(t(implementation))
influencetr <- as.data.frame(t(influence))

#add rank to dataframes and sort
friendstr[,"rank"] <-rank(-friendstr[,"Total"], ties.method = "average")
friendstr1 <-friendstr[order(friendstr$rank, decreasing=FALSE), ]

advicetr[,"rank"] <-rank(-advicetr[,"Total"], ties.method = "average")
advicetr1 <-advicetr[order(advicetr$rank, decreasing=FALSE), ]

creativitytr[,"rank"] <-rank(-creativitytr[,"Total"], ties.method = "average")
creativitytr1 <-creativitytr[order(creativitytr$rank, decreasing=FALSE), ]

implementationtr[,"rank"] <-rank(-implementationtr[,"Total"], ties.method = "average")
implementationtr1 <- implementationtr[order(implementationtr$rank, decreasing=FALSE), ]

influencetr[,"rank"] <-rank(-influencetr[,"Total"], ties.method = "average")
influencetr1 <- influencetr[order(influencetr$rank, decreasing=FALSE), ]

#guestlist preference

#1 exclusive 2 expansive 3 tight
guestlist <-as.data.frame(fulldata[,"guestlist"])
guestlist[,"id"] <- c(1:60)

```

```{r}

#manipulate cosine order table to add ranks

#cosine.order[,"creativity.cs.rank"] <-rank(cosine.order[,"Friend_Creativity"], ties.method = "min")
#cosine.order[,"influence.cs.rank"] <-rank(cosine.order[,"Friend_Influence"], ties.method = "min")
#cosine.order[,"implementation.cs.rank"] <-rank(cosine.order[,"Friend_Implementation"], ties.method = "min")
cosine.order[,"average.cs.rank"] <-rank(cosine.order[,"Average"], ties.method = "average")

#order via id
cosine.order <- cosine.order[order(cosine.order$id, decreasing=FALSE), ]


```


## Weighted Analysis

Lobbying

Weighting:
Advice: 0.30 
Influence: 0.40 
Cosine similiarity: 0.25 
Friends: 0.05

```{r}

#filter out expansive or exclusive
b <- c(1,2,3)
df4 <- guestlist[guestlist[,1] %in% b,]

#for the above people, pull advice and influence scores and ranks and create table

values <- df4$id #list of people

lob10 <- advicetr[values, 61:62]
lob10 <- rename(lob10[,1:2], c("Total"="advice_total", "rank"="advice_rank"))
lob10[,"advice.weighted.rank"] <- lob10$advice_rank * 0.30
lob20 <- influencetr[values,61:62]
lob20 <- rename(lob20[,1:2], c("Total"="influence_total", "rank"="influence_rank"))
lob20[,"influence.weight.rank"] <- lob20$influence_rank * 0.40
summarytable01 <- cbind(lob10, lob20)


#add cosine similiarity to table for influence and average
summarytable01 <- cbind(summarytable01,cosine.order[values, c(9)])
summarytable01 <- rename(summarytable01, c("cosine.order[values, c(9)]"="cs_avg_rank"))
summarytable01[,"cs_avg_rank.weighted"] <- summarytable01$cs_avg_rank * 0.25

#add friend to table
summarytable01 <-cbind(summarytable01, friendstr[values,61:62])
summarytable01 <-rename(summarytable01, c("Total"="friends_total", "rank"="friends_rank"))
summarytable01[,"friends_rank.weighted"] <- summarytable01$friends_rank * 0.05

#sum up all criteria and rank
summarytable01[, "total"] <- rowSums(summarytable01[,c(3,6,8,11)]) 
summarytable01[,"total.rank"] <-rank(summarytable01[,"total"], ties.method = "min")



#sort based on total.rank
summarytable01 <- summarytable01[order(summarytable01$total.rank, decreasing=FALSE), ]

print(summarytable01)

 
```


Creativity

Weighting:
Advice: 0.30 
Creativity: 0.40
Cosine similiarity: 0.25 
Friends: 0.05


```{r}

#filter out cohesive
c <- c(1,2,3)
df5 <- guestlist[guestlist[,1] %in% c,]

#for the above people, pull advice and creativity scores and ranks and create table

values11 <- df5$id #list of people

creat11 <- advicetr[values11, 61:62]
creat11 <- rename(creat11[,1:2], c("Total"="advice_total", "rank"="advice_rank"))
creat11[,"advice.weighted.rank"] <- creat11$advice_rank * 0.30
creat21 <- creativitytr[values11,61:62]
creat21 <- rename(creat21[,1:2], c("Total"="creativity_total", "rank"="creativity_rank"))
creat21[,"influence.weighted.rank"] <- creat21$creativity_rank * 0.40
summarytable11 <- cbind(creat11, creat21)


#add cosine similiarity to table for influence and average
summarytable11 <- cbind(summarytable11,cosine.order[values11, c(9)])
summarytable11 <- rename(summarytable11, c("cosine.order[values11, c(9)]"="cs_avg_rank"))
summarytable11["cs_avg_rank.weighted"] <- summarytable11$cs_avg_rank * 0.25

#add friend to table
summarytable11 <-cbind(summarytable11, friendstr[values11,61:62])
summarytable11 <-rename(summarytable11, c("Total"="friends_total", "rank"="friends_rank"))
summarytable11[,"friends_rank.weighted"] <- summarytable11$friends_rank * 0.05


#sum up criteria
summarytable11[, "total"] <- rowSums(summarytable11[,c(3,6,8,11)])
summarytable11[,"total.rank"] <-rank(summarytable11[,"total"], ties.method = "min")

#sort based on total.rank
summarytable11 <- summarytable11[order(summarytable11$total.rank, decreasing=FALSE), ]

print(summarytable11)

```









Implementation

Weighting:
Advice: 0.35 
Influence: 0.35 
Cosine similiarity: 0.2 
Friends: 0.1

```{r}

#filter out cohesive
a <- c(1,2,3)
df3 <- guestlist[guestlist[,1] %in% a,]

#for the above people, pull advice and implementation scores and ranks and create table

values21 <- df3$id #list of people

implem11 <- advicetr[values21, 61:62]
implem11 <- rename(implem11[,1:2], c("Total"="advice_total", "rank"="advice_rank"))
implem11[,"advice.weighted.rank"] <- implem11$advice_rank * 0.35
implem21 <- implementationtr[values21,61:62]
implem21 <- rename(implem21[,1:2], c("Total"="implementation_total", "rank"="implementation_rank"))
implem21[,"influence.weighted.rank"] <- implem21$implementation_rank * 0.35
summarytable21 <- cbind(implem11, implem21)


#add cosine similiarity to table for influence and average
summarytable21 <- cbind(summarytable21,cosine.order[values21, c(9)])
summarytable21 <- rename(summarytable21, c("cosine.order[values21, c(9)]"="cs_avg_rank"))
summarytable21["cs_avg_rank.weighted"] <- summarytable21$cs_avg_rank * 0.2

#add friend to table
summarytable21 <-cbind(summarytable21, friendstr[values21,61:62])
summarytable21 <-rename(summarytable21, c("Total"="friends_total", "rank"="friends_rank"))
summarytable21[,"friends_rank.weighted"] <- summarytable21$friends_rank * 0.1

#sum up criteria
summarytable21[, "total"] <- rowSums(summarytable21[,c(3,6,8,11)])
summarytable21[,"total.rank"] <-rank(summarytable21[,"total"], ties.method = "min")

#sort based on total.rank
summarytable21 <- summarytable21[order(summarytable21$total.rank, decreasing=FALSE), ]

print(summarytable21)

```








