---
title: "Cecilia_AiB - picking teams"
author: "Cecilia Nok Sze Cheung"
date: "11 December 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Steven's stuff


```{r setup, include=FALSE}
library(reshape2)
library(lsa)
library(ggplot2)
library(pander)
```

```{r echo=FALSE}
# load data
picks.data <- read.csv("peoplepickinganonymised.csv")
```

```{r echo=FALSE}
# a bit of exploratory analysis

sequence <- c(0,60,120,240)
count <- 0

for (i in 1:60) {
  count <- 1
  for (j in sequence) {
    assign(paste("candidate", i, count , sep=""), picks.data[, 3+i+j])
    count <- count + 1
  }
  
}

#paste("id",1,sep = '')

```

```{r echo=FALSE}
# cosine similarity

# first create an empty matrix that will be populated with the cosine similarity results
mat.cosine <- matrix(0, 60, 5)
mat.cosine2 <- matrix(0, 60, 5)

# subset data to only include the picks
sub.data <- picks.data[, 4:length(picks.data)]

# calculate cosine similarity and populate matrix
for (id in 1:nrow(sub.data)) {
  
  # extract all the vectors needed to calculate the cosine similarities
  friend <- as.numeric(sub.data[id, 1:60])   # skip the influence picks
  creativity <- as.numeric(sub.data[id, 121:180])
  influence <- as.numeric(sub.data[id, 181:240])
  implementation <- as.numeric(sub.data[id, 241:300])
  
  # populate cosine matrix
  mat.cosine[id,2] <- cosine(friend, friend)
  mat.cosine[id,3] <- cosine(friend, creativity)
  mat.cosine[id,4] <- cosine(friend, influence)
  mat.cosine[id,5] <- cosine(friend, implementation)
}

# manual calculation for cosine similarity
cosine.sim <- function(x,y) {
  x %*% y / sqrt(x%*%x * y%*%y)
}

# check if results are the same using built function
for (id in 1:nrow(sub.data)) {
  
  # extract all the vectors needed to calculate the cosine similarities
  friend <- as.numeric(sub.data[id, 1:60])   # skip the influence picks
  creativity <- as.numeric(sub.data[id, 121:180])
  influence <- as.numeric(sub.data[id, 181:240])
  implementation <- as.numeric(sub.data[id, 241:300])
  
  # populate cosine matrix
  mat.cosine2[id,2] <- cosine.sim(friend, friend)
  mat.cosine2[id,3] <- cosine.sim(friend, creativity)
  mat.cosine2[id,4] <- cosine.sim(friend, influence)
  mat.cosine2[id,5] <- cosine.sim(friend, implementation)
}

# mat.cosine == mat.cosine2, returns TRUE

# calculate the mean cosine similarity for each ID, without Friend_Friend column
means <- rowMeans(mat.cosine[,3:5])

# combine means to cosine matrix
mat.cosineM <- cbind(mat.cosine, means)

# convert to dataframe, add column names, populate ID column
data.cosine <- data.frame(mat.cosineM)

names <- c("id", "Friend_Friend", "Friend_Creativity", "Friend_Influence", "Friend_Implementation", "Average")
colnames(data.cosine) <- names

data.cosine$id <- 1:60

# order "average" decreasing
cosine.order <- data.cosine[order(-data.cosine$Average),]

# z-score function
z.score <- function(x, mean, sd) {
  (x - mean) / sd
}

# mean of cosine scores
mean.cosine <- mean(cosine.order$Average, na.rm = TRUE)

# sd of cosine scores
sd.cosine <- sd(cosine.order$Average, na.rm = TRUE)

# apply z-score function to calculate z-score
cosine.order$Z.score <- sapply(cosine.order$Average, z.score, mean = mean.cosine,sd=sd.cosine)
```

```{r echo=FALSE, fig.width = 10, fig.align = "center"}
# create bins in cosine.order
cosine.order$bin <- cut(cosine.order$Average, breaks = 5, labels = c("(0,0.2]","(0.2,0.4]", "(0.4,0.6]","(0.6,0.8]","(0.8,1]"))

# plot histogram of average cosine similarities
ggplot(na.omit(cosine.order), aes(bin, fill = bin)) +
  geom_bar() +
  labs(x = "Cosine Similarity", y = "Count", title = "Average Cosine Similarity Frequency") +
  scale_fill_brewer(palette = "Blues",direction = -1, guide=FALSE)
```

The graph above shows the average cosine similarity for each ID. As can be seen, over 20 IDs display a high level of flexibility in picking teams for different tasks. The average cosine similarity was calculated using each IDs social picks as benchmark. These picks were then compared to each IDs picks for different tasks. Three IDs have an average cosine similarity of 1, indicating very low levels of flexibility. 

```{r echo=FALSE, fig.width = 10, fig.align = "center", fig.height=8}
# plot each IDs average cosine score
ggplot(na.omit(cosine.order), aes(x = reorder(factor(id), Average), y = Average, fill = Average)) +
  geom_bar(stat="identity") +
  coord_flip() +
  labs(x = "ID", y = "Average Cosine Similarity", title = "Average Cosine Similarity by ID") +
  scale_fill_distiller(palette = "Blues", guide=FALSE, direction = 1)
```

```{r echo=FALSE, fig.align="center"}
# subset cosine table to only include ID, average, z-score
cosine.table <- cosine.order[, c("id","Average","Z.score")]
panderOptions("digits", 3)
pander(cosine.table)

### write.csv(cosine.order, file = "cosine.csv")
```



## Analysis - picking leaders

```{r}
library(reshape2)
library(plyr)

```


```{r}
fulldata <- read.csv("peoplepickinganonymised.csv")
```


```{r}
#cleaning up and wrangling data

#add row to sum up columns
fulldata <-as.numeric(fulldata)
fulldata[, c(1:303)] <- sapply(fulldata[, c(1:303)], as.numeric)
fulldata["Total",] <- colSums(fulldata)

#make seperate df for each component
friends <- fulldata[,4:63] 
advice <- fulldata[,64:123]
creativity <- fulldata[,124:183]
implementation <- fulldata[,184:243]
influence <- fulldata[,244:303]

#transform dataframes and turn back into df
friendstr <- as.data.frame(t(friends))
advicetr <- as.data.frame(t(advice))
creativitytr <- as.data.frame(t(creativity))
implementationtr <- as.data.frame(t(implementation))
influencetr <- as.data.frame(t(influence))

#add rank to dataframes and sort
friendstr[,"rank"] <-rank(-friendstr[,"Total"], ties.method = "min")
friendstr1 <-friendstr[order(friendstr$rank, decreasing=FALSE), ]

advicetr[,"rank"] <-rank(-advicetr[,"Total"], ties.method = "min")
advicetr1 <-advicetr[order(advicetr$rank, decreasing=FALSE), ]

creativitytr[,"rank"] <-rank(-creativitytr[,"Total"], ties.method = "min")
creativitytr1 <-creativitytr[order(creativitytr$rank, decreasing=FALSE), ]

implementationtr[,"rank"] <-rank(-implementationtr[,"Total"], ties.method = "min")
implementationtr1 <- implementationtr[order(implementationtr$rank, decreasing=FALSE), ]

influencetr[,"rank"] <-rank(-influencetr[,"Total"], ties.method = "min")
influencetr1 <- influencetr[order(influencetr$rank, decreasing=FALSE), ]

#guestlist preference

#1 exclusive 2 expansive 3 tight
guestlist <-as.data.frame(fulldata[,"guestlist"])
guestlist[,"id"] <- c(1:61)

```

```{r}


#manipulate cosine order table to add ranks

cosine.order[,"creativity.cs.rank"] <-rank(cosine.order[,"Friend_Creativity"], ties.method = "min")
cosine.order[,"influence.cs.rank"] <-rank(cosine.order[,"Friend_Influence"], ties.method = "min")
cosine.order[,"implementation.cs.rank"] <-rank(cosine.order[,"Friend_Implementation"], ties.method = "min")
cosine.order[,"average.cs.rank"] <-rank(cosine.order[,"Average"], ties.method = "min")


```



## Lobbying

Criteria:
- needs to be expansive/exclusive
- good at giving advice and peers must view this person as influential
- flexible when picking teams
- has decent amount of friends 

```{r}

#filter out expansive or exclusive
x <- c(1,2)
df <- guestlist[guestlist[,1] %in% x,]

#for the above people, pull advice and influence scores and ranks and create table

values <- df$id #list of people

lob1 <- advicetr[values, 61:62]
lob2 <- influencetr[values,61:62]
lob3 <- cbind(lob1, lob2)
lob4 <- rename(lob3[,1:2], c("Total"="advice_total", "rank"="advice_rank"))
lob5 <- rename(lob3[,3:4], c("Total"="influence_total", "rank"="influence_rank"))
summarytable <- cbind(lob4, lob5)

#add cosine similiarity to table for influence and average
summarytable <- cbind(summarytable,cosine.order[values, c(10,12)])
summarytable[, "total"] <- rowSums(summarytable[,c(2,4:6)])
summarytable[,"total.rank"] <-rank(summarytable[,"total"], ties.method = "min")

#friend check
summarytable <-cbind(summarytable, friendstr[values,61:62])
summarytable <-rename(summarytable, c("Total"="friends_total", "rank"="friends_rank"))

#sort based on total.rank
summarytable <- summarytable[order(summarytable$total.rank, decreasing=FALSE), ]


print(summarytable)

```

When looking at this table, we can narrow it down to person 33 - who appears to have a good balance of the different criteria that we look at, and also happens to have a decent number of friends as well.

## Creativity

Criteria:
- needs to be expansive
- good at giving advice and peers must view this person as creative
- flexible when picking teams
- has decent amount of friends 

```{r}

#filter out expansive
y <- 2
df1 <- guestlist[guestlist[,1] %in% y,]

#for the above people, pull advice and influence scores and ranks and create table

values1 <- df1$id #list of people

creat1 <- advicetr[values1, 61:62]
creat2 <- creativitytr[values1,61:62]
creat3 <- cbind(creat1, creat2)
creat4 <- rename(creat3[,1:2], c("Total"="advice_total", "rank"="advice_rank"))
creat5 <- rename(creat3[,3:4], c("Total"="creativity_total", "rank"="creativity_rank"))
summarytable1 <- cbind(creat4, creat5)

#add cosine similiarity to table for influence and average
summarytable1 <- cbind(summarytable1,cosine.order[values1, c(9,12)])
summarytable1[, "total"] <- rowSums(summarytable1[,c(2,4:6)])
summarytable1[,"total.rank"] <-rank(summarytable1[,"total"], ties.method = "min")

#friend check
summarytable1 <-cbind(summarytable1, friendstr[values1,61:62])
summarytable1 <-rename(summarytable1, c("Total"="friends_total", "rank"="friends_rank"))

#sort based on total.rank
summarytable1 <- summarytable1[order(summarytable1$total.rank, decreasing=FALSE), ]


print(summarytable1)

```

Leader: 21

## Implementation

Criteria:
- needs to be cohesive
- good at giving advice and peers must view this person as good at implementation
- flexible when picking teams
- has decent amount of friends 


```{r}

#filter out cohesive
z <- 3
df2 <- guestlist[guestlist[,1] %in% z,]

#for the above people, pull advice and implementation scores and ranks and create table

values2 <- df2$id #list of people

implem1 <- advicetr[values2, 61:62]
implem2 <- creativitytr[values2,61:62]
implem3 <- cbind(implem1, implem2)
implem4 <- rename(implem3[,1:2], c("Total"="advice_total", "rank"="advice_rank"))
implem5 <- rename(implem3[,3:4], c("Total"="implementation_total", "rank"="implementation_rank"))
summarytable2 <- cbind(implem4, implem5)

#add cosine similiarity to table for influence and average
summarytable2 <- cbind(summarytable2,cosine.order[values2, c(11,12)])
summarytable2[, "total"] <- rowSums(summarytable2[,c(2,4:6)])
summarytable2[,"total.rank"] <-rank(summarytable2[,"total"], ties.method = "min")

#friend check
summarytable2 <-cbind(summarytable2, friendstr[values2,61:62])
summarytable2 <-rename(summarytable2, c("Total"="friends_total", "rank"="friends_rank"))

#sort based on total.rank
summarytable2 <- summarytable2[order(summarytable2$total.rank, decreasing=FALSE), ]

print(summarytable2)

```

Leader: Person 19

(thinking whether i should add weights to the different criteria?)









