---
title: "Group Project"
author: "Louise Fallon"
date: "6 December 2016"
output: html_document
---

```{r}
library(igraph)
library(knitr)
library(xlsx)

```

```{r}
fulldata <- read.csv("peoplepickinganonymised.csv")
```

```{r}
dffrmatrix <- fulldata[,4:63]
frmatrix <- as.matrix(dffrmatrix)
```

```{r}
G <- graph_from_adjacency_matrix(frmatrix, mode = "directed",add.colnames = TRUE, diag=FALSE)
```

#Plotting

basic plot with R 
```{r}
coords <- layout_(G, nicely())
plot(G, vertex.size=12, edge.arrow.size=0.2)
```

Plot with some more parameters

```{r}
plot(G, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.color="darkblue",
     vertex.label.family="Helvetica")
```

Random layout

```{r}
plot(G, layout = layout_randomly, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.color="darkblue",
     vertex.label.family="Helvetica")
```

Sphere layout

```{r}
l <- layout_on_sphere(G)
plot(G, layout=l, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.color="darkblue",
     vertex.label.family="Helvetica")
```

Kamada-Kawai layout (quite nice I think)

```{r}
l <- layout_with_kk(G)
plot(G, layout=l, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.color="darkblue",
     vertex.label.family="Helvetica")
```


Fruchterman Reingold layout (best for displaying communities and cliques)

```{r}
l <-layout.fruchterman.reingold(G)
plot(G, layout=l, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.color="darkblue",
     vertex.label.family="Helvetica")
```


# Communities

```{r}
com <- cluster_spinglass(G, spin=5)
V(G)$color <- com$membership+1
G <- set_graph_attr(G, "layout", layout.fruchterman.reingold(G))
plot(G, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.label.family="Helvetica")
```

```{r}
com <- cluster_edge_betweenness(G)
V(G)$color <- com$membership+1
G <- set_graph_attr(G, "layout", layout.fruchterman.reingold(G))
plot(G, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.label.family="Helvetica")
```

```{r}
com <- cluster_leading_eigen(G)
V(G)$color <- com$membership+1
G <- set_graph_attr(G, "layout", layout.fruchterman.reingold(G))
plot(G, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.label.family="Helvetica")
```

```{r}
com <- cluster_walktrap(G)
V(G)$color <- com$membership+1
G <- set_graph_attr(G, "layout", layout.fruchterman.reingold(G))
plot(G, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.label.family="Helvetica")
```

Fast Greedy clustering (treats as undirected)
```{r}
cfg <- cluster_fast_greedy(as.undirected(G))

plot(cfg, as.undirected(G), vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.family="Helvetica")
```


```{r}
com <- cluster_infomap(G)
V(G)$color <- com$membership+1
G <- set_graph_attr(G, "layout", layout.fruchterman.reingold(G))
plot(G, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.label.family="Helvetica")
```

##Cliques

```{r warning=FALSE}
G.cli <- cliques(G, min = 5, max = NULL)

# Set subgraph members
clique1 <- as.vector(G.cli[[1]])
clique2 <- as.vector(G.cli[[2]])
clique3 <- as.vector(G.cli[[3]])
clique4 <- as.vector(G.cli[[4]])

# Add edge attribute id values
E(G)$id <- seq(ecount(G))

# Extract supgraph
sg.c1 <- induced.subgraph(graph=G,vids=clique1)
sg.c1.Id <- E(sg.c1)$id
sg.c2 <- induced.subgraph(graph=G,vids=clique2)
sg.c2.Id <- E(sg.c2)$id
sg.c3 <- induced.subgraph(graph=G,vids=clique3)
sg.c3.Id <- E(sg.c3)$id
sg.c4 <- induced.subgraph(graph=G,vids=clique4)
sg.c4.Id <- E(sg.c4)$id

# Set graph and subgraph edge and node colors and sizes
E(G)$color="grey"
V(G)$color="darkgray" 
V(G)$label.color="white"
E(G)[sg.c1.Id]$color <- "green"
V(G)[clique1]$color <- "green"
E(G)[sg.c2.Id]$color <- "red"
V(G)[clique2]$color <- "red"
E(G)[sg.c3.Id]$color <- "orange"
V(G)[clique3]$color <- "orange"
E(G)[sg.c4.Id]$color <- "blue"
V(G)[clique4]$color <- "blue"
# Set seed value
set.seed(40041)

# Set layout options
l <- layout_as_tree(G)

# Plot graph and subgraph
plot.igraph(x=G,layout=l, vertex.size=15, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.family="Helvetica")

#Reset graph parameters
E(G)$color="grey"
V(G)$color="darkblue" 
```

We can see for the 4 largest cliques (of size 5), the orange and red clique are overlapping (node 54 is in red but not orange, and node 55 is in orange but not red).

```{r echo=FALSE}
cluster <- c("green","yellow","yellow","blue")
clique <- c("green","red","orange","blue")
clustertoclique <- data.frame(cluster=cluster, clique=clique)
kable(clustertoclique)
```

# Other Questions

Plot for friend graph with size = in degree.

```{r}
set.seed(48)
layoutfr <- layout.fruchterman.reingold(G)
```

```{r}
G.degree <- degree(G, mode="in")
G <- set_graph_attr(G, "layout", layoutfr)
plot(G, vertex.size=G.degree*2, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.label.color="white", vertex.label.family="Helvetica")
```

Advice Graph 

```{r echo=FALSE}
dfadvmatrix <- fulldata[,64:123]
advmatrix <- as.matrix(dfadvmatrix)
```

```{r echo=FALSE}
G.adv <- graph_from_adjacency_matrix(advmatrix, mode = "directed",add.colnames = TRUE, diag=FALSE)
```

```{r echo=FALSE}
G.adv.degree <- degree(G.adv, mode="in")
G.adv <- set_graph_attr(G.adv, "layout", layoutfr)
plot(G.adv, vertex.size=G.adv.degree*2, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.color="darkblue", vertex.label.color="white", vertex.label.family="Helvetica")
```

Creative Graph 
```{r echo=FALSE}
dfcrmatrix <- fulldata[,124:183]
crmatrix <- as.matrix(dfcrmatrix)
```

```{r echo=FALSE}
G.cr <- graph_from_adjacency_matrix(crmatrix, mode = "directed",add.colnames = TRUE, diag=FALSE)
```

```{r echo=FALSE}
G.cr.degree <- degree(G.cr, mode="in")
G.cr <- set_graph_attr(G.cr, "layout", layoutfr)
plot(G.cr, vertex.size=G.cr.degree*2, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.color="darkblue", vertex.label.color="white", vertex.label.family="Helvetica")
```

Implementation Graph 

```{r echo=FALSE}
dfimpmatrix <- fulldata[,184:243]
impmatrix <- as.matrix(dfimpmatrix)
```

```{r echo=FALSE}
G.imp <- graph_from_adjacency_matrix(impmatrix, mode = "directed",add.colnames = TRUE, diag=FALSE)
```

```{r echo=FALSE}
G.imp.degree <- degree(G.imp, mode="in")
G.imp <- set_graph_attr(G.imp, "layout", layoutfr)
plot(G.imp, vertex.size=G.imp.degree*2, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.color="darkblue", vertex.label.color="white", vertex.label.family="Helvetica")
```

Influence  Graph 

```{r echo=FALSE}
dfinflmatrix <- fulldata[,244:303]
inflmatrix <- as.matrix(dfinflmatrix)
```

```{r echo=FALSE}
G.infl <- graph_from_adjacency_matrix(inflmatrix, mode = "directed",add.colnames = TRUE, diag=FALSE)
```

```{r echo=FALSE}
G.infl.degree <- degree(G.infl, mode="in")
G.infl <- set_graph_attr(G.infl, "layout", layoutfr)
plot(G.infl, vertex.size=G.infl.degree*2, edge.arrow.size=0.2, edge.width=0.2, vertex.label.cex=0.42, vertex.color="darkblue", vertex.label.color="white", vertex.label.family="Helvetica")
```

# Network Measures

The most basic set of measures would be the in degree for each of the relevant questions.

Below is a table with the **ranking** of nodes by in degree for each of the questions.

```{r}
indegreetable <- data.frame(
          friendship    =order(G.degree, decreasing = TRUE),
          advice        =order(G.adv.degree, decreasing = TRUE),
          creativity    =order(G.cr.degree, decreasing = TRUE),
          influence     =order(G.infl.degree, decreasing = TRUE),
          implementation=order(G.imp.degree, decreasing = TRUE))
kable(indegreetable)
```


Focusing on the three main questions, and to trade this off against "cost", we simply divide by the in-degree of the friendship question. Below are the rankings that occur after this transformation. We can see that #27 is at the top, because this node had an in degree of 0 for the friendship question. To remove this anomaly we set the in degree artificially to 0.5.

```{r}
G.degree[27] <- 0.5
indegreetable <- data.frame(
          creativity    =order(G.cr.degree/G.degree, decreasing = TRUE),
          influence     =order(G.infl.degree/G.degree, decreasing = TRUE),
          implementation=order(G.imp.degree/G.degree, decreasing = TRUE))
kable(indegreetable)
```

To see how these rankings are formed, the raw data is included into the table 

```{r}
G.degree[27] <- 0.5
indegreetable <- data.frame(
          creativity    =order(G.cr.degree/G.degree, decreasing = TRUE),
          frienddegree.cr  =as.integer(G.degree[order(G.cr.degree/G.degree, decreasing=TRUE)]),
          crdegree      =as.integer(G.cr.degree[order(G.cr.degree/G.degree, decreasing=TRUE)]),
          influence     =order(G.infl.degree/G.degree, decreasing = TRUE),
          frienddegree.infl  =as.integer(G.degree[order(G.infl.degree/G.degree, decreasing=TRUE)]),
          infldegree    =as.integer(G.infl.degree[order(G.infl.degree/G.degree, decreasing=TRUE)]),
          implementation=order(G.imp.degree/G.degree, decreasing = TRUE),
          frienddegree.imp  =as.integer(G.degree[order(G.imp.degree/G.degree, decreasing=TRUE)]),
          impldegree    =as.integer(G.imp.degree[order(G.imp.degree/G.degree, decreasing=TRUE)]))
kable(indegreetable)
```

There are also network-specific properties that are important for the choice of teams. Below rankings are created from weighted averages of standardised metrics, including network proporties from the friendship graph.

For the **Design** team it would be useful to have:

* High leverage - high betweenness centrality 
* Percieved creativity - higher weighting on in degree centrality of the creativity network
* Either large or medium sized parties
* Expansive > Exclusive > Tight party invites

```{r}
dfpartymatrix <- fulldata[,1:3]
levels(dfpartymatrix$style) <- c("cosy","mixer","party")
levels(dfpartymatrix$guestlist) <- c("exclusive","expansive","tight")
```

```{r}
##define metric for design team based on party choices, from stage/style matrix in slides
dfpartymatrix$designpartymetric <- 0
##add party type metrics
dfpartymatrix$designpartymetric[dfpartymatrix$guestlist == "exclusive"] <- 2
dfpartymatrix$designpartymetric[dfpartymatrix$guestlist == "expansive"] <- 3
dfpartymatrix$designpartymetric[dfpartymatrix$guestlist == "tight"] <- 1
##add party size metrics
dfpartymatrix$designpartymetric[dfpartymatrix$style == "cosy"] <- dfpartymatrix$designpartymetric[dfpartymatrix$style == "cosy"] + 1
dfpartymatrix$designpartymetric[dfpartymatrix$style == "mixer"] <- 
dfpartymatrix$designpartymetric[dfpartymatrix$style == "mixer"] + 3
dfpartymatrix$designpartymetric[dfpartymatrix$style == "expansive"] <- dfpartymatrix$designpartymetric[dfpartymatrix$style == "expansive"] + 3
```

```{r}
standardise <- function(x){(x-min(x))/(max(x)-min(x))}

fr.btwn.centr <- as.numeric(betweenness(G))

creativitymetric <- (standardise(fr.btwn.centr)*0.2 + 
                       standardise(G.cr.degree)*0.6 +
                      standardise(dfpartymatrix$designpartymetric)*0.2)/standardise(G.degree)

designtable <- data.frame(
          node   =order(creativitymetric, decreasing = TRUE),
          creativitymetric =creativitymetric[order(creativitymetric, decreasing=TRUE)],
          creativitydegree =as.integer(G.cr.degree[order(creativitymetric, decreasing=TRUE)]),
          frienddegree  =as.integer(G.degree[order(creativitymetric, decreasing=TRUE)]),
          btwncentrality = fr.btwn.centr[order(creativitymetric, decreasing=TRUE)])
kable(designtable)
```

For the **Lobbying** team it would be useful to have:

* High influence - high eigenvector centrality 
* Percieved influence - in degree centrality of the influence network
* Large > medium > small sized parties
* Exclusive or Expansive > Tight party invites

```{R}
dfpartymatrix$lobbypartymetric <- 0
##add party type metrics
dfpartymatrix$lobbypartymetric[dfpartymatrix$guestlist == "exclusive"] <- 3
dfpartymatrix$lobbypartymetric[dfpartymatrix$guestlist == "expansive"] <- 3
dfpartymatrix$lobbypartymetric[dfpartymatrix$guestlist == "tight"] <- 1
##add party size metrics
dfpartymatrix$lobbypartymetric[dfpartymatrix$style == "cosy"] <- dfpartymatrix$lobbypartymetric[dfpartymatrix$style == "cosy"] + 1
dfpartymatrix$lobbypartymetric[dfpartymatrix$style == "mixer"] <- 
dfpartymatrix$lobbypartymetric[dfpartymatrix$style == "mixer"] + 2
dfpartymatrix$lobbypartymetric[dfpartymatrix$style == "expansive"] <- dfpartymatrix$lobbypartymetric[dfpartymatrix$style == "expansive"] + 3
```

```{r}
fr.eign.centr <- as.numeric(eigen_centrality(G)$vector)

influencemetric <- (standardise(fr.eign.centr)*0.4 + 
                      standardise(G.infl.degree)*0.4 +
                      standardise(dfpartymatrix$lobbypartymetric)*0.2
                         )/standardise(G.degree)
influencemetric[27] <- NaN


lobbytable <- data.frame(
          node   =order(influencemetric, decreasing = TRUE),
          influencemetric =influencemetric[order(influencemetric, decreasing=TRUE)],
          influencedegree =as.integer(G.infl.degree[order(influencemetric, decreasing=TRUE)]),
          frienddegree  =as.integer(G.degree[order(influencemetric, decreasing=TRUE)]),
          eigncentrality = fr.eign.centr[order(influencemetric, decreasing=TRUE)])
kable(lobbytable)
```

For the **Implementation** team it would be useful to have:

* High cohesion - high closeness centrality 
* Percieved implementation skills - in degree centrality of the implementation network
* Small > medium > large sized parties
* Tight > Exclusive > Expansive  party invites

```{r}
dfpartymatrix$implpartymetric <- 0
##add party type metrics
dfpartymatrix$implpartymetric[dfpartymatrix$guestlist == "exclusive"] <- 2
dfpartymatrix$implpartymetric[dfpartymatrix$guestlist == "expansive"] <- 1
dfpartymatrix$implpartymetric[dfpartymatrix$guestlist == "tight"] <- 3
##add party size metrics
dfpartymatrix$implpartymetric[dfpartymatrix$style == "cosy"] <- dfpartymatrix$implpartymetric[dfpartymatrix$style == "cosy"] + 3
dfpartymatrix$implpartymetric[dfpartymatrix$style == "mixer"] <- 
dfpartymatrix$implpartymetric[dfpartymatrix$style == "mixer"] + 2
dfpartymatrix$implpartymetric[dfpartymatrix$style == "expansive"] <- dfpartymatrix$implpartymetric[dfpartymatrix$style == "expansive"] + 1
```

```{r}
fr.cls.centr <- closeness(G)

implementationmetric <- (standardise(fr.cls.centr)*0.2 +
                         standardise(G.imp.degree)*0.6 +
                         standardise(dfpartymatrix$implpartymetric)*0.2
                         )/standardise(G.degree)
implementationmetric[27] <- NaN

impltable <- data.frame(
          node   =order(implementationmetric, decreasing = TRUE),
          implementationmetric =implementationmetric[order(implementationmetric, decreasing=TRUE)],
          influencedegree =as.integer(G.infl.degree[order(implementationmetric, decreasing=TRUE)]),
          frienddegree  =as.integer(G.degree[order(implementationmetric, decreasing=TRUE)]),
          closenesscentrality = fr.cls.centr[order(implementationmetric, decreasing=TRUE)])
kable(impltable)
```

```{r echo=FALSE, eval=FALSE}
tabletoexport <- data.frame(
  node = 1:60,
  
  frienddegree = G.degree,
  creativitydegree = G.cr.degree,
  influencedegree = G.infl.degree,
  implementationdegree = G.imp.degree,
  cluster = as.integer(V(G)$color),

  creativitymetric = creativitymetric*standardise(G.degree),
  scaledcreativitymetric = creativitymetric,
  
  influencemetric = influencemetric*standardise(G.degree),
  scaledinfluencemetric = influencemetric,
  
  implementationmetric = implementationmetric*standardise(G.degree),
  scaledimplementationmetric = implementationmetric
  
)
write.xlsx(tabletoexport, "AinBOptimisationdata.xlsx")
```

##Notes

* tkplot doesn't work well on mac computers (requires Xquartz and loads the graph outside of the file.)
* Spin clustering (4 or 5 spins) provides a very similar result to leading eigenvector clustering and walking trap clustering in this case
* louvain community detection only works for undirected graphs (same with fast_greedy)
* There are no maximally connected cliques of 6
* layout_with_kk makes a nice layout, but layout.fruchterman.reingold puts the clusters together nicely.