---
title: "ainb_group"
author: "Steven Locorotondo"
date: "12/8/2016"
output: html_document
---

```{r setup, include=FALSE}
library(reshape2)
library(lsa)
library(ggplot2)
library(pander)
```

```{r echo=FALSE}
# load data
picks.data <- read.csv("peoplepickinganonymised.csv")
```

```{r echo=FALSE}
# a bit of exploratory analysis

sequence <- c(0,60,120,240)
count <- 0

for (i in 1:60) {
  count <- 1
  for (j in sequence) {
    assign(paste("candidate", i, count , sep=""), picks.data[, 3+i+j])
    count <- count + 1
  }
  
}

#paste("id",1,sep = '')

```

```{r echo=FALSE}
# cosine similarity

# first create an empty matrix that will be populated with the cosine similarity results
mat.cosine <- matrix(0, 60, 5)
mat.cosine2 <- matrix(0, 60, 5)

# subset data to only include the picks
sub.data <- picks.data[, 4:length(picks.data)]

# calculate cosine similarity and populate matrix
for (id in 1:nrow(sub.data)) {
  
  # extract all the vectors needed to calculate the cosine similarities
  friend <- as.numeric(sub.data[id, 1:60])   # skip the influence picks
  creativity <- as.numeric(sub.data[id, 121:180])
  influence <- as.numeric(sub.data[id, 181:240])
  implementation <- as.numeric(sub.data[id, 241:300])
  
  # populate cosine matrix
  mat.cosine[id,2] <- cosine(friend, friend)
  mat.cosine[id,3] <- cosine(friend, creativity)
  mat.cosine[id,4] <- cosine(friend, influence)
  mat.cosine[id,5] <- cosine(friend, implementation)
}

# manual calculation for cosine similarity
cosine.sim <- function(x,y) {
  x %*% y / sqrt(x%*%x * y%*%y)
}

# check if results are the same using built function
for (id in 1:nrow(sub.data)) {
  
  # extract all the vectors needed to calculate the cosine similarities
  friend <- as.numeric(sub.data[id, 1:60])   # skip the influence picks
  creativity <- as.numeric(sub.data[id, 121:180])
  influence <- as.numeric(sub.data[id, 181:240])
  implementation <- as.numeric(sub.data[id, 241:300])
  
  # populate cosine matrix
  mat.cosine2[id,2] <- cosine.sim(friend, friend)
  mat.cosine2[id,3] <- cosine.sim(friend, creativity)
  mat.cosine2[id,4] <- cosine.sim(friend, influence)
  mat.cosine2[id,5] <- cosine.sim(friend, implementation)
}

# mat.cosine == mat.cosine2, returns TRUE

# calculate the mean cosine similarity for each ID, without Friend_Friend column
means <- rowMeans(mat.cosine[,3:5])

# combine means to cosine matrix
mat.cosineM <- cbind(mat.cosine, means)

# convert to dataframe, add column names, populate ID column
data.cosine <- data.frame(mat.cosineM)

names <- c("id", "Friend_Friend", "Friend_Creativity", "Friend_Influence", "Friend_Implementation", "Average")
colnames(data.cosine) <- names

data.cosine$id <- 1:60

# order "average" decreasing
cosine.order <- data.cosine[order(-data.cosine$Average),]

# z-score function
z.score <- function(x, mean, sd) {
  (x - mean) / sd
}

# mean of cosine scores
mean.cosine <- mean(cosine.order$Average, na.rm = TRUE)

# sd of cosine scores
sd.cosine <- sd(cosine.order$Average, na.rm = TRUE)

# apply z-score function to calculate z-score
cosine.order$Z.score <- sapply(cosine.order$Average, z.score, mean = mean.cosine,sd=sd.cosine)
```

```{r echo=FALSE, fig.width = 10, fig.align = "center"}
# create bins in cosine.order
cosine.order$bin <- cut(cosine.order$Average, breaks = 5, labels = c("(0,0.2]","(0.2,0.4]", "(0.4,0.6]","(0.6,0.8]","(0.8,1]"))

# plot histogram of average cosine similarities
ggplot(na.omit(cosine.order), aes(bin, fill = bin)) +
  geom_bar() +
  labs(x = "Cosine Similarity", y = "Count", title = "Average Cosine Similarity Frequency") +
  scale_fill_brewer(palette = "Blues",direction = -1, guide=FALSE)
```

The graph above shows the average cosine similarity for each ID. As can be seen, over 20 IDs display a high level of flexibility in picking teams for different tasks. The average cosine similarity was calculated using each IDs social picks as benchmark. These picks were then compared to each IDs picks for different tasks. Three IDs have an average cosine similarity of 1, indicating very low levels of flexibility. 

```{r echo=FALSE, fig.width = 10, fig.align = "center", fig.height=8}
# plot each IDs average cosine score
ggplot(na.omit(cosine.order), aes(x = reorder(factor(id), Average), y = Average, fill = Average)) +
  geom_bar(stat="identity") +
  coord_flip() +
  labs(x = "ID", y = "Average Cosine Similarity", title = "Average Cosine Similarity by ID") +
  scale_fill_distiller(palette = "Blues", guide=FALSE, direction = 1)
```

```{r echo=FALSE, fig.align="center"}
# subset cosine table to only include ID, average, z-score
cosine.table <- cosine.order[, c("id","Average","Z.score")]
panderOptions("digits", 3)
pander(cosine.table)

### write.csv(cosine.order, file = "cosine.csv")
```

### notes
- create histogram to show the distribution of average cosine sim

